Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-02 draft.tex
fix refs / expand dataset section
more experimental results for explanations

\def\student{Jaocb LaRock}
\def\studentno{1667321}
\def\place{Siegen}
\def\Date{31.03.2025} 
\def\semester{6}

@@

	concerns about its potential misuse in areas such as politics, entertainment, and national

@@

	they made a particular decision, what factors influenced it, and how confident they are in

@@

		\cite{muller_does_2022}.

@@

					also considered perceptible, and used in the same research instead use the
					amplitudes at each fundamental frequency period. Their purpose is to capture
					irregular vocal fold vibrations which may be an indication but not a guarantee
					of a synthetic voice.

@@

				Simple & expand pitch-flucs & until 10000 & 93.31 & 0.05661

@@

@@

@@

	having little, no, or negative impact on the end classification with the exception of jitter

>>>>

\def\student{Jaocb LaRock}
\def\studentno{1667321}
\def\place{Siegen}
\def\Date{17.03.2025} 
\def\semester{6}

@@

	concerns about its potential misuse in areas such as politics, entertainment and national

@@

	they made a particular decision, what factors influenced it and how confident they are in

@@

		\cite{muller_does_2022}. I have chosen it for these experiments because of the
		aforementioned focus on generalization, its relative recency, compared to some others and
		the fact that it has also been used previously by some other experiments, which provides a
		useful perspective against which I can compare my method.

@@

					also considered perceptible and are used in the same research. They instead
					make use of the amplitudes at each fundamental frequency period. Their purpose
					is to capture irregular vocal fold vibrations which may be an indication but
					not a guarantee of a synthetic voice.

@@

				Simple & expand pitch\-flucs & until 10000 & 93.31\% & 0.05661 \\
				3 hidden layers & expand pitch\-flucs & until 10000 & 93.87\% & 0.05317

@@

				HNRs & 0.2667 & -0.0788 \\
				mel spectrogram & 0.0982 & -0.0434 \\
				MFCC & 0.2879 & 0.2408 \\
				f0 lengths & 0.1690 & -0.0521 \\
				onset strengths & 0.1384 & -0.0613 \\
				intensities & 0.1576 & -0.0504 \\
				jitter features & 0.1444 & 0.0118 \\
				shimmer features & 0.1747 & 0.0116
			pitch fluctuation features and a complex terminus}
			\label{table:exp-results-mpf-cterm}

@@

		\subsubsection{Model with Expanded Pitch-Fluctuation Features and Complex Terminus}
		The model with multiple pitch-fluctuation features in combination with a terminus
		containing multiple hidden layers fared similarly to the other two, this time with the
		pitch fluctuations having not influence on the outcome whatsoever. Unlike the previous
		examples, the trust value of the intensities feature was negative here.

@@

	having little, no or negative impact on the end classification with the exception of jitter
